---
title: "test_202010flights_1000"
author: '605194735'
date: "1/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=FALSE, warning = FALSE)
```

```{r packages, include=FALSE}
# loading packages I might need
library(plyr)
library(tidyverse)
library(ggplot2)
library(mosaic)
library(car)
library(gmodels)
library(readxl)
library(lubridate) #to separate date/time
library(plotly) #interactive graphics
```


```{r data}
# loading dataset

flights202010_1000 <- read_csv("/Users/katemcinerny/Documents/UCLA/Carceral_ecologies/heli_data/data/csv/flights202010_1000.csv")
```

## Summary Stats

```{r summary altitude}
favstats(flights202010_1000$flights.positions.altitude)
```

Thoughts: the min altitude of 250 ft is very low-- even lower than the departing airport altitude of 550 feet.
I'm curious: Is there a way to graphically see the path of how altitudes change? Or mainly just map it? Curious whether the lower altitudes are concentrated in takeoff/landing or if they hover over certain neighborhoods…

Is there a limit on how high or low helicopters should fly? How does the median of 850 ft impact noise levels, compared to min/ max?

Which law enforcement agency's helicopters are flying the lowest? (I hypothesize sherrifs, but who knows)

Then later on.... Want to look at where in the county they fly the lowest vs. highest.

Also, what should I do about missing values?
Is the max a true max or is it an outlier that I should exclude?




```{r summary speed}
favstats(flights202010_1000$flights.positions.groundSpeed)

```
Again, is the max a typo?


## Parse date/time
```{r describe date-time}

str(flights202010_1000)
```


```{r parse date-time}

d <- as.POSIXct(flights202010_1000$flights.positions.timestamp, format="%Y-%m-%d %H:%M:%S")
flights202010_1000$flights.positions.date_km <- format(d, format="%Y-%m-%d")
flights202010_1000$flights.positions.time_km <- format(d, format="%H:%M:%S")
flights202010_1000$flights.positions.hour_km <- format(d, format="%H")

View(flights202010_1000)
```



Graph altitude over time
group by the call sign

```{r altitude over time}
p <- ggplot(data=flights202010_1000, aes(x=flights.positions.timestamp, y=flights.positions.altitude, group=flights.callsign)) + geom_line() 
p

```

## Interactive plot

```{r interactive}

fig <- plot_ly(flights202010_1000, x= ~flights.positions.timestamp)
fig <- fig %>% add_trace(y= ~flights.positions.altitude, name= 'altitude', mode= 'lines')

fig
```

# Time of day

```{r time}

# how to show count of points per hour of day? gonna have to do this with a bigger dataset w/ different flights

timecounts <- table(flights202010_1000$flights.positions.time_km)
barplot(timecounts, main="Frequent Flight Times", xlab="Time of day")
```

```{r}
p <- ggplot(data=flights202010_1000, aes(x=flights.positions.hour_km, group=flights.aircraftRegistration)) + geom_bar() 
p
```

